Reconstructing Propositional Proofs in Type Theory

### 2017-10-27 paper/sections/abstract.tex
Last changes in the Paper (#37)
* minor changes.

* [ paper ] section 2 improvements.

* [ paper ] major changes, abstract, conclusions was added.

* [ paper ] minor changes, title and abstract.

* [ paper ] fixing some mistakes.

* [ paper ] fixing error grammars and adding notes.

* [ paper ] section 3 introduction added.

* [ paper ] appendix added.

* added text.

* [ paper ] perliminaries added.

* [ paper ] implementation added, some proofs added.

* [ paper ] fixing some typos and text added.

* [ paper ] fixing some typos and text added.

* [ paper ] complexity measure added.

* [ pape

% ===================================================================

\begin{abstract}
We describe a syntactical proof-reconstruction
approach to verify proofs generated by \Metis prover to problems in
classical propositional logic.
To verify these \Metis proofs, we developed a tool able to translate
such derivations to \Agda proof-terms.
We formulate in type theory each inference rule found
in \Metis derivations. This allowed us to type-check with \Agda, \Metis proofs
step-by-step. We leave it for future work,
the opportunity to extend this work to support other provers, proof assistants, and formalisms.

\keywords{proof-reconstruction, type theory, automatic theorem prover,
proof-assistant}

\end{abstract}

>>>>

\begin{abstract}
We describe a syntactical proof-reconstruction approach to verify proofs
generated by \Metis prover to problems in classical propositional logic.
To verify these \Metis proofs, we developed a tool able to translate such
derivations to \Agda proof-terms. We formalise in type theory each inference
rule found in \Metis derivations. This allowed us to type-check with \Agda,
\Metis proofs step-by-step. We leave it for future work, the opportunity to
extend this work to support other provers, proof-assistants, and formalisms.

\keywords{proof-reconstruction, type theory, automatic theorem prover,
proof-assistant}
\end{abstract}

### 2017-10-27 paper/sections/proof-reconstruction.tex
[ paper ] proof-assistant and proof-term.

The proof-reconstruction approach proposed consists of a series of
steps similar to the workflow presented~\cite{sultana2015}.  This
process is a translation from a source system to a target system. In
our case, the system of origin, the automatic theorem prover, is
\Metis; the target system is a proof assistant, \Agda. We choose
\Agda, but another proof assistant with the same support of type
theory and inductive types could be used.

>>>>

The proof-reconstruction approach proposed consists of a series of
steps similar to the workflow presented~\cite{sultana2015}.  This
process is a translation from a source system to a target system. In
our case, the system of origin, the automatic theorem prover, is
\Metis; the target system is a proof-assistant, \Agda. We choose
\Agda, but another proof-assistant with the same support of type
theory and inductive types could be used.

### 2017-10-27 paper/sections/related-work.tex
[ paper ] proof-assistant and proof-term.

Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
We found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
certified checker for proof witness coming from the \SMT solver
\name{veriT}~\cite{bouton2009} and adds a new tactic named verit, that calls
\name{veriT} on any \name{Coq} goal. Also for \name{Coq}, given a fixed but
arbitrary first-order signature, \citeauthor{Bezem2002} in \cite{Bezem2002}
transform a proof produced by the first-order automatic theorem prover
\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof term.

There are some successful attempts using proof assistants for classical logic
instead of type theory.
Let us mention some representative of such tools. This descriptions is
mainly based on~\citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.

The \name{Isabelle} proof assistant has the \name{Sledgehammer} tool.
This program provides a full integration between
automatic theorem provers~\cite{blanchette2013extending,Fleury2014,bohme2010} and
\name{Isabelle/HOL}~\cite{nipkow2002isabelle}, the specialization of
\name{Isabelle} for higher-order logic.
A modular proof-reconstruction workflow is presented jointly with
the full integration of \name{Leo-II} and \name{Satallax} provers with
\name{Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.

>>>>

Another important proof-assistant in type theory is \name{Coq}~\cite{coqteam}.
We found the \name{SMTCoq}~\cite{armand2011,Ekici2017} tool which provides a
certified checker for proof witness coming from the \SMT solver
\name{veriT}~\cite{bouton2009} and adds a new tactic named verit, that calls
\name{veriT} on any \name{Coq} goal. Also for \name{Coq}, given a fixed but
arbitrary first-order signature, \citeauthor{Bezem2002} in \cite{Bezem2002}
transform a proof produced by the first-order automatic theorem prover
\name{Bliksem}~\cite{deNivelle2003} in a \name{Coq} proof-term.

There are some successful attempts using proof-assistants for classical logic
instead of type theory.
Let us mention some representative of such tools. This descriptions is
mainly based on~\citeauthor{Sicard-Ramirez2016}~\cite{Sicard-Ramirez2016}.

The \name{Isabelle} proof-assistant has the \name{Sledgehammer} tool.
This program provides a full integration between
automatic theorem provers~\cite{blanchette2013extending,Fleury2014,bohme2010} and
\name{Isabelle/HOL}~\cite{nipkow2002isabelle}, the specialization of
\name{Isabelle} for higher-order logic.
A modular proof-reconstruction workflow is presented jointly with
the full integration of \name{Leo-II} and \name{Satallax} provers with
\name{Isabelle/HOL} in \citeauthor{Een2004}~\cite{Een2004}.
